Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-31 paper/paper.tex
quick pass on results

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases where the anomaly has
been detected in during the execution of test code or its close
%% the rationale we provide is related to the above; not crashes
neighborhood. The rationale is that the test in this group executed
without violating any internal checks of the API. In constrast,
warnings in the LO group reflect the cases where the anomaly was
observed during the execution of functions from standard JS libraries\Fix{check}.
  We found that different engines often check pre-conditions of
those functions differently. It can happen, for example, that one
engine enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
%% \Igor{these cases happen because the specification describes how a function
%% should work, however the internal implementation is defined by the
%% engine developers}\Mar{If you confirm that there is no code in specs
%%   (see comment above), what would be those abstract
%%   functions/interfaces that you mentioned to me the other day?}.
In those cases, our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the fuzzed test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only \Fix{12\%} of the reals bugs
we found originated from the LO category.

@@

In this study, we analyzed the impact of two orthogonal dimensions in
bug finding: test mining and fuzzing. The first dimension focuses on
the impact of new inputs in bug finding whereas the second dimension
focuses on the impact of variations of existing inputs in bug finding.

@@

In this experiment, we ran all tests (see Section~\ref{sec:seeds})
using our infrastructure in no-fuzzing mode. We inspected all warnings
reported by our tool and, for those we found suspicious, we filed a
bug report in the corresponding bug tracker.

>>>>

\Mar{explain what is a bucket (we refer to it later).}
The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases where the anomaly has
been detected in during the execution of test code or its close
%% the rationale we provide is related to the above; not crashes
neighborhood. The rationale is that the test in this group executed
without violating any internal checks of the API. In constrast,
warnings in the LO group reflect the cases where the anomaly was
observed during the execution of functions from standard JS libraries\Fix{check}.
  We found that different engines often check pre-conditions of
those functions differently. It can happen, for example, that one
engine enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
%% \Igor{these cases happen because the specification describes how a function
%% should work, however the internal implementation is defined by the
%% engine developers}\Mar{If you confirm that there is no code in specs
%%   (see comment above), what would be those abstract
%%   functions/interfaces that you mentioned to me the other day?}.
In those cases, our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the fuzzed test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only \Fix{12\%} of the reals bugs
we found originated from the LO category.

@@

The overarching goal of our study is to identify the ability of simple
techniques to find bugs in \js\ engines with cross-engine differential
testing.  We analyzed the impact of two orthogonal dimensions: test
mining and fuzzing. The first dimension focuses on the impact of
inputs, mined from the web, in bug finding whereas the second
dimension focuses on the impact of fuzzing these inputs in bug
finding.

We describe the methodology we used in this experiment in the
following. Recall that our tool produces warnings on output organized
in buckets (Section~\ref{sec:design}). Each bucket describes a
warnings--one per file (fuzzed or not)--and can be of ``lo'' or ``hi''
importance, according to the heuristic we
defined. Figure~\ref{fig:distribution} shows the distribution of
warnings reported per bucket. Observe that in some cases the number of
files per bucket is very high; it would be infeasible to manually
inspect all of them. For that, we inspected each and every reported
bucket but only one file per bucket. For the cases we found
suspicious, we filed a bug report in the bug tracker. In some cases,
we used the Mozila lithium tool~\cite{lithium} to minimize the test
case. Table~\ref{tab:summary-of-results} summarizes the number of
buckets of each category per execution mode. \Fix{elaborate}

\begin{table}[t]
  \centering
  \caption{\label{tab:summary-of-results}Summary of results.}
  \begin{tabular}{ccrr}
    \toprule
    mode & type & \# buckets & \% positive buckets \\ 
    \midrule
    \multirow{2}{*}{no-fuzz} & lo & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} \\
                             & hi & \Fix{.} & \Fix{.} \\    
    \bottomrule     
  \end{tabular}
\end{table}

@@

In this experiment, we ran all tests (see Section~\ref{sec:seeds})
using our infrastructure in no-fuzzing mode. The goal is to identify
the impact of using publicly available tests on ..........
